Inferring true changes in microbial abundance from taxonomically-biased microbiome measurements

### 2022-01-16 abundance-measurement.Rmd
Add support for Word export
The following changes now allow the document to be successfully exported
to Word (.docx) format. Several problems remain in the output document;
many equations don't render properly and equation and figure numbering
and referencing do not work correctly.

- Update method of including images to be consistent in all figure chunks
- Adjust the `include_svg()` to have an else clause to handle Word export
- Add 'word' option to Makefile

```{r error-proportions, out.width = '90%', fig.cap = '(ref:cap-error-proportions)', cache = TRUE}
svg_path <- "figures/illustrations/error-proportions.svg"
if (knitr::is_html_output()) {
  fig_path <- svg_path
} else if (knitr::is_latex_output()) {
  fig_path <- svg_to_pdf(svg_path)
}
knitr::include_graphics(fig_path)
rm(svg_path, fig_path)
```

>>>>

```{r error-proportions, out.width = '90%', fig.cap = '(ref:cap-error-proportions)', cache = TRUE}
"figures/illustrations/error-proportions.svg" %>%
  include_svg
```

### 2022-01-16 case-studies.Rmd
Add support for Word export
The following changes now allow the document to be successfully exported
to Word (.docx) format. Several problems remain in the output document;
many equations don't render properly and equation and figure numbering
and referencing do not work correctly.

- Update method of including images to be consistent in all figure chunks
- Adjust the `include_svg()` to have an else clause to handle Word export
- Add 'word' option to Makefile

```{r momspi-mean-efficiency-dist, fig.cap = '(ref:cap-momspi-mean-efficiency-dist)'}
svg_path <- fs::path(
  "notebook/_posts/2021-11-01-momspi-summary/momspi-summary_files", 
  "figure-html5/momspi-mean-efficiency-dist-1.svg"
)
if (knitr::is_html_output()) {
  fig_path <- svg_path
} else if (knitr::is_latex_output()) {
  fig_path <- svg_to_pdf(svg_path)
}
knitr::include_graphics(fig_path)
rm(svg_path, fig_path)
```

>>>>

```{r momspi-mean-efficiency-dist, fig.cap = '(ref:cap-momspi-mean-efficiency-dist)'}
fs::path(
  "notebook/_posts/2021-11-01-momspi-summary/momspi-summary_files", 
  "figure-html5/momspi-mean-efficiency-dist-1.svg"
  ) %>%
  include_svg
```

### 2022-01-16 differential-abundance.Rmd
Add support for Word export
The following changes now allow the document to be successfully exported
to Word (.docx) format. Several problems remain in the output document;
many equations don't render properly and equation and figure numbering
and referencing do not work correctly.

- Update method of including images to be consistent in all figure chunks
- Adjust the `include_svg()` to have an else clause to handle Word export
- Add 'word' option to Makefile

```{r regression-example, fig.cap = '(ref:regression-example)'}
svg_path <- here::here(
  "notebook/_posts/2021-08-03-simulate-regression-example/",
  "simulate-regression-example_files/figure-html5",
  "main-figure-1.svg"
)
if (knitr::is_html_output()) {
  fig_path <- svg_path
} else if (knitr::is_latex_output()) {
  fig_path <- svg_to_pdf(svg_path)
}
knitr::include_graphics(fig_path)
rm(svg_path, fig_path)
```

>>>>

```{r regression-example, fig.cap = '(ref:regression-example)'}
here::here(
  "notebook/_posts/2021-08-03-simulate-regression-example/",
  "simulate-regression-example_files/figure-html5",
  "main-figure-1.svg"
  ) %>%
  include_svg
```

### 2022-01-16 introduction.Rmd
Add support for Word export
The following changes now allow the document to be successfully exported
to Word (.docx) format. Several problems remain in the output document;
many equations don't render properly and equation and figure numbering
and referencing do not work correctly.

- Update method of including images to be consistent in all figure chunks
- Adjust the `include_svg()` to have an else clause to handle Word export
- Add 'word' option to Makefile

```{r basic-problem, fig.cap = '(ref:cap-basic-problem)'}
# NOTE: call to include_graphics() has to be in top level expression
svg_path <- fs::path(
  "notebook/_posts/2021-10-27-illustrate-the-problem/illustrate-the-problem_files", 
  "figure-html5/brooks_lcrisp_prop_and_fc-1.svg"
)
if (knitr::is_html_output()) {
  fig_path <- svg_path
} else if (knitr::is_latex_output()) {
  fig_path <- svg_to_pdf(svg_path)
}
knitr::include_graphics(fig_path)
rm(svg_path, fig_path)
```

>>>>

```{r basic-problem, fig.cap = '(ref:cap-basic-problem)'}
# NOTE: call to include_graphics() has to be in top level expression
fs::path(
  "notebook/_posts/2021-10-27-illustrate-the-problem/illustrate-the-problem_files", 
  "figure-html5/brooks_lcrisp_prop_and_fc-1.svg"
  ) %>%
  include_svg
```

### 2022-01-16 solutions.Rmd
Add support for Word export
The following changes now allow the document to be successfully exported
to Word (.docx) format. Several problems remain in the output document;
many equations don't render properly and equation and figure numbering
and referencing do not work correctly.

- Update method of including images to be consistent in all figure chunks
- Adjust the `include_svg()` to have an else clause to handle Word export
- Add 'word' option to Makefile

```{r calibration-example, fig.cap = '(ref:cap-calibration-example)', out.width = '100%'}
fig_path <- fs::path(
  "notebook/_posts/2021-10-25-brooks2015thet-calibration",
  "brooks2015thet-calibration_files/figure-html5/brooks2015thet_fc_calibration-1.png"
)
knitr::include_graphics(fig_path)
rm(fig_path)
```

>>>>

```{r calibration-example, fig.cap = '(ref:cap-calibration-example)', out.width = '100%'}
fs::path(
  "notebook/_posts/2021-10-25-brooks2015thet-calibration",
  "brooks2015thet-calibration_files/figure-html5/brooks2015thet_fc_calibration-1.png"
) %>%
  knitr::include_graphics()
```
